Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

The results by LM10 would place then the dark matter halo of our Milky
Way as an extreme outlier in the $\Lambda$ CDM model. 
This extreme prolateness also correlateswith the extreme
triaxiality of the 11 classical satellites of the MW ($c/a\approx
0.2$, and $b/a\approx0.9$) with an spatial distribution 
also oriented perpendicular to the MW plane, another highly unusual
feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}

{\bf Comparison against observations.}

{\bf Implications for observational studies in our Galaxy}

>>>>

The results by LM10 would place then the dark matter halo of our Milky
Way as an extreme outlier in the $\Lambda$ CDM model. 
This extreme prolateness also correlates with the extreme
triaxiality of the 11 classical satellites of the MW ($c/a\approx
0.2$, and $b/a\approx0.9$) with an spatial distribution 
also oriented perpendicular to the MW plane, another highly unusual
feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}

From the results presented in this work we advance the idea that the
twisting shells in the density is a feature that deserves to be
explored in the process of constraining shape parameters from tidal
stream data. 
The current parameterizations of coaxial density/potential shells
might be too rigid.
The inclusion of a new free parameter describing this degree of
twisting might relax the conflict between the observational
constraints and the numerical results.
